Sparse Function-space Representation \\ of Neural Networks

### 2023-05-17 paper/main.tex
CL bit

	% Import table content
	\input{tables/cl_table_1}
\end{wraptable}
%
% Overview

We aim to highlight our sparse representation's ability to retain prior knowledge for continual learning (CL) (as in \cref{sec:sequential}). We consider the single-head (SH) setting that is harder and more realistic than multi-head (MH)~\citep{van2019three}.	 \todo{can't find the bibtex for their NIPS workshop paper} % typically hard and more competitive \cite{}
%
% Benchmarks/architectures
 Our \our-based regularizer is evaluated on three CL benchmarks, specifically Split-MNIST (S-MNIST), Split-FashionMNIST (S-FMNIST), and the 10-tasks Permuted-MNIST (P-MNIST). We adhere to the same setups as outlined in \cite{rudner2022continual, pan2020continual}, which involve utilizing a two-layer MLP with 256 hidden units and ReLU activation for S-MNIST and S-FMNIST, and a two-layer MLP with 100 hidden units for P-MNIST, to ensure consistency. Please refer to \cref{app:cl-exp} for full details.

% Methods
We compare our method against two categories of methods: {\em (i)}~weight-regularization methods: EWC, SI, and VCL (which additionally incorporates coresets), and {\em(ii)}~function-based regularization methods: DER, FROMP, S-FSVI, SFR. We also introduce an ablation study where we replace $\bar{\MB_t}^{-1}$ with an identity matrix $\MI_M$, equivalent to assuming a GP with i.i.d.\ prior with a unit variance (giving an L2 regularizer).
Following \cite{rudner2022continual}, we use 200 points per tasks. Additionally,  we consider only 40 points for S-MNIST, to investigate if our method was still capable of capture more information due to its sparse formulation.

%% Comments on the results:
\cref{tbl:cl_table_1} shows results
We get the best results on S-MNIST both 40 and 200 pts. per task

On S-FMNIST we are on par with DER, which is however exploiting a reservoir buffer technique, that iteratively samples new "inducing points"

On P-MNIST we are lower than S-FSVI, however % I'm still running experiments, so we can hope that it is not the best overall in the end

>>>>

	% Import table content
	\input{tables/cl_table_1}
\end{wraptable}
%
% Overview
We aim to highlight our sparse representation's ability to retain previous knowledge for continual learning (CL) (as in \cref{sec:sequential}). We consider the single-head (SH) setting that is harder and more realistic than multi-head (MH)~\citep{van2019three}.	 \todo{can't find the bibtex for their NIPS workshop paper} % typically hard and more competitive \cite{}
%
% Benchmarks/architectures
 Our \our-based regularizer is evaluated on three CL benchmarks, specifically Split-MNIST (S-MNIST), Split-FashionMNIST (S-FMNIST), and the 10-tasks Permuted-MNIST (P-MNIST). We adhere to the same setups as outlined in \cite{rudner2022continual, pan2020continual}, which involve utilizing a two-layer MLP with 256 hidden units and ReLU activation for S-MNIST and S-FMNIST, and a two-layer MLP with 100 hidden units for P-MNIST, to ensure consistency. Please refer to \cref{app:cl-exp} for full details.

% Methods
We compare our method against two categories of methods: {\em (i)}~weight-regularization methods: EWC, SI, and VCL (which additionally incorporates coresets), and {\em(ii)}~function-based regularization methods: DER, FROMP, S-FSVI, SFR. We also introduce an ablation study where we replace $\bar{\MB}_t^{-1}$ with an identity matrix $\MI_M$, equivalent to using an L2 regularizer.
In \cref{tbl:cl_table_1}, we use 200 points for each task, and we further demonstrate our method's ability to compress information to a low number of points in S-MNIST.

%% Comments on the results:
From \cref{tbl:cl_table_1}, it is clear that the weight-space regularization methods completely fail compared to the function-space methods on S-MNIST and S-FMNIST, but are comparable on P-MNIST. %, commonly referred as Domain Incremental Learning. (opposed to the Class-Incremental Learning for S-MNIST and S-FMNIST)
Considering only function-space methods, we can see that \our achieves the best results on most datasets, and is particularly effective, when using fewer points per task.
On S-FMNIST, our method obtains close results to DER, which regularizes the model by taking the mean squared error between current and old function outputs without accounting the covariance structure of the loss similar to our L2 ablation. Moreover, their method exploits reservoir sampling \citep{vitter1985random} to obtain a continuously updated set inducing points.
S-FSVI obtains the best on P-MNIST, but with the downside of requiring high computational costs based on performing variational inference, compared to \our. \todo{on PMNIST our method is not really super-fast, so that could be not the best thing to say here} % we could also say that P-MNIST is known to be a bad/ill-posed dataset for CL 
Finally, it is worth noticing as our ablation already provides a very solid baseline consistently over all datasets.
